% !TEX root = ../Thesis.tex
\thispagestyle{empty}
\hfill
\vfill
\noindent Copyright Notice:

\noindent This document is licensed under the Creative Commons Attribution-Non-Commercial-No derivative works 2.5 Switzerland license: \href{http://creativecommons.org/licenses/by-nc-nd/2.5/ch/}{creative\-commons.org/licenses/by-nc-nd/2.5}.

\noindent You are free to copy, distribute, display, and perform of this work under the following conditions:
\begin{itemize}
	\item You must give the original author credit.
	\item You may not use this work for commercial purposes.
	\item You may not alter, transform, or build upon this work.
	\item Chapters~\ref{ch:xrm2008}, \ref{ch:tsuda2008} and \ref{ch:haberthuer2010} of this work are publications authored for several journals. Chapter \ref{ch:xrm2008} was published as an open access proceeding in the \emph{\href{http://dx.doi.org/10.1088/1742-6596/186/1/012040}{Journal of Physics: Conference Series}} and is freely distributable. Chapters \ref{ch:tsuda2008} and \ref{ch:haberthuer2010} were published in the \emph{\href{http://dx.doi.org/10.1152/japplphysiol.90546.2008}{Journal of Applied Physiology}} and the \emph{\href{http://dx.doi.org/10.1107/S0909049510019618}{Journal of Synchrotron Radiation}}, respectively. Both these chapters are covered by copyright from their Journals.
\end{itemize}
\noindent For any reuse or distribution, you must take clear to others the license terms of this work. Any of these conditions can be waived if you get permission from the copyright holder. Nothing in this license impairs or restricts the author’s moral rights according to Swiss law. 
 
\noindent The detailed license agreement can be found at: \href{http://creativecommons.org/licenses/by-nc-nd/2.5/ch/legalcode.de}{creativecommons.org/ licenses/by-nc-nd/2.5/ch/legalcode.de}
 
 \vfill

\noindent\myName\\\mbox{\emph{\myTitle}}\\\myDegree\\\myVersion
\bigskip

\noindent\spacedlowsmallcaps{Supervisors}:\\
\myProf \\
\myOtherProf \\ 
\mySupervisor
\medskip

\noindent\spacedlowsmallcaps{Location}:\\
\noindent\myLocation
\medskip

\noindent\spacedlowsmallcaps{Time Frame}:\\
September 2006--\myTime